Demographic inference under the coalescent as an ill-posed nonlinear inverse problem

### 2019-04-23 manuscript/main.tex
ramp based on TMRCA CDF with constant approximation, cc #8
Kelley's equation

\author{
W. DeWitt$^{1}$, K. Harris$^{2}$, and K. Harris$^{1}$\\
\small{Departments of $^1$Genome Sciences and $^2$Biology, University of Washington, Seattle, USA}\\
% \small{$^\ast$ Equal contribution}
}

@@

We must deal with the asymptotically constant boundary condition.
Standard regularizers blow up on the infinite epoch.
Let's use half Gaussian instead of Lebesgue measure on time to induce integrability: $\mathrm{d}\mu(t) = \frac{\sqrt{2}}{\sqrt{\pi}\tau}\exp\left(-\frac{1}{2}\left(\frac{t}{\tau}\right)^2\right)\mathrm{d}t,$
where $\tau$ is the characteristic time to asmptopia (the boundary of our time grid).
For example, a modified $L2$ would be
\[
R\left[\eta(t)\right] = \int_0^\infty \eta(t)^2 \mathrm{d}\mu(t) = \frac{\sqrt{2}}{\sqrt{\pi}\tau}\int_0^\infty \eta(t)^2 \exp\left(-\frac{1}{2}\left(\frac{t}{\tau}\right)^2\right)\mathrm{d}t.
\]
So the discretized problem is expressed in terms of the error function $\erf(\cdot)$ if $\eta(t)$ is piecewise constant.
This will give extra (but finite) weight / penalty to the infinite epoch based on the survival function of $\mathrm{d}\mu(t)$.
We can tune how much weight the boundary epoch gets by tuning the width of the Gaussian.

>>>>

\author{
W. DeWitt$^{1}$, K. Harris$^{2}$, and K. Harris$^{1}$\\
\small{Departments of $^1$Genome Sciences and $^2$Biology, University of Washington, Seattle, USA}
% \small{$^\ast$ Equal contribution}
}

@@

% Kelley's eqn
In real data (or realistic simulations) the time region where the SFS has lost information is determined by the expected number of coalescent trees $\rho\ell$, where $\rho$ is the recombination rate and $\ell$ is the genome size.
For $t$ such that the expected number of trees that have $T_{\text{MRCA}} > t$ becomes less that one, the SFS does not contain information beyond $t$.
To wit,
\[
\mathbb{P}\left(T_{\text{MRCA}}>t\right) < \frac{1}{\rho \ell}.
\]
The P\&K model doesn't model finite genome size, so it makes sense to use the CDF of $T_{\text{MRCA}}$ in that setting.

% We must deal with the asymptotically constant boundary condition.
% Standard regularizers blow up on the infinite epoch.
% Let's use half Gaussian instead of Lebesgue measure on time to induce integrability: $\mathrm{d}\mu(t) = \frac{\sqrt{2}}{\sqrt{\pi}\tau}\exp\left(-\frac{1}{2}\left(\frac{t}{\tau}\right)^2\right)\mathrm{d}t,$
% where $\tau$ is the characteristic time to asmptopia (the boundary of our time grid).
% For example, a modified $L2$ would be
% \[
% R\left[\eta(t)\right] = \int_0^\infty \eta(t)^2 \mathrm{d}\mu(t) = \frac{\sqrt{2}}{\sqrt{\pi}\tau}\int_0^\infty \eta(t)^2 \exp\left(-\frac{1}{2}\left(\frac{t}{\tau}\right)^2\right)\mathrm{d}t.
% \]
% So the discretized problem is expressed in terms of the error function $\erf(\cdot)$ if $\eta(t)$ is piecewise constant.
% This will give extra (but finite) weight / penalty to the infinite epoch based on the survival function of $\mathrm{d}\mu(t)$.
% We can tune how much weight the boundary epoch gets by tuning the width of the Gaussian.
